Reproducible development environments with rix

### 2023-12-23 paper.qmd
appendix

## The Nix package manager

@@

## Reproducible development environments with Nix

@@

The above call to `rix()` generates an expression that installs several
[R]{.proglang} packages ([AER]{.pkg} version 1.2-8 gets installed, which is an
older version of the package. If the user didn't not specify the version, the
version available as of the `nixpkgs` commit would be used), but also install
several TeXLive packages for authoring documents with \LaTeX, the development
versions of [rix]{.pkg} and [fusen]{.pkg} (downloaded from Github), and finally
the RStudio integrated development environment.

@@

## More technical details {#sec-techdetails .unnumbered}

>>>>

## The Nix package manager {#sec-nix}

@@

## Reproducible development environments with Nix {#sec-repro-nix}

@@

The above call to `rix()` generates an expression that installs several
[R]{.proglang} packages ([AER]{.pkg} version 1.2-8 gets installed, which is an
older version of the package. Had the user not specified the version, the
version available as of the `nixpkgs` commit would be used), but also install
several TeXLive packages for authoring documents with \LaTeX, the development
versions of [rix]{.pkg} and [fusen]{.pkg} (downloaded from Github), and finally
the RStudio integrated development environment. It should be noted that as of
writing, RStudio is not available on macOS through `nixpkgs`, so the above
expression will only work on Windows and Linux distributions. To make the
expression work on macOS, the "rstudio" string could be replaced by "code",
which would install VS Code instead, or "other", to use any other editor
such as Emacs or Vi.

@@

## Appendix {#sec-appendix .unnumbered}

Here is the Nix expression generated from the call to the `rix()`
function of section #sec-repro-nix:

```{r}
rix(r_ver = "4.3.1",
    r_pkgs = c("dplyr", "chronicler", "AER@1.2-8"),
    system_pkgs = c("quarto", "git"),
    tex_pkgs = c(
          "amsmath",
          "framed",
          "fvextra",
          "environ",
          "fontawesome5",
          "orcidlink",
          "pdfcol",
          "tcolorbox",
          "tikzfill"
    ),
    git_pkgs = list(
                 list(package_name = "rix",
                   repo_url = "https://github.com/b-rodrigues/rix/",
                   branch_name = "master",
                   commit = "ea92a88ecdfc2d74bdf1dde3e441d008521b1756"),
                 list(package_name = "fusen",
                   repo_url = "https://github.com/ThinkR-open/fusen",
                   branch_name = "main",
                   commit = "d617172447d2947efb20ad6a4463742b8a5d79dc")
    ),
    ide = "rstudio",
    project_path = tempfile(),
    overwrite = TRUE)
```
